Analysis of split plot design using MCMCglmm

### 2020-07-30 README.Rmd
Back to MCMCglmm we go
Update README
Paper is knitted to MS Word, not PDF
fix code formatting in README
another code formatting change in README
Update instructions for using Docker

- the manuscript as submitted (in PDF format) and it's Rmd source file

@@

A Docker image is a lightweight GNU/Linux virtual computer that can be run as a piece of software on Windows and OSX (and other Linux systems).
To capture the complete computational environment used for this project we have a Dockerfile that specifies how to make the Docker image that we developed this project in.
The Docker image includes all of the software dependencies needed to run the code in this project, as well as the R package and other compendium files.
To launch the Docker image for this project, first, [install Docker](https://docs.docker.com/installation/) on your computer.
At the Docker prompt, enter:

    docker run -dp 8787:8787 adamhsparks/rice-awd-shb

>>>>

- the manuscript as submitted (in MS Word format) and it's Rmd source file

@@

A Docker image is a lightweight GNU/Linux virtual computer that can be run as a piece of software on Windows and OSX (and other Linux systems).
To capture the complete computational environment used for this project we have a Dockerfile that specifies how to make the Docker image that we developed this project in.
The Docker image includes all of the software dependencies needed to run the code in this project, as well as the R package and other compendium files.
To launch the Docker image for this project, first, [install Docker](https://docs.docker.com/installation/) on your computer.
Then at a command line prompt, use the following commands to start the instance.

```bash
docker pull adamhsparks/rice-awd-shb:main
docker run -dp 8787:8787 rice-awd-shb
```
